Untitled

### 2024-10-23 code/manuscript_altanalysis.Rmd
making figures

# df.temptemp <- df.temptemp %>% 
#   left_join(uds.cw %>% filter(Year == 2011) %>% select(BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>% 
#   mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
#                     (STATE %in% c('PA','IN','AK') & Year >= 2015) |
#                     (STATE %in% c('MT','LA') & Year >= 2016) |
#                     (STATE %in% c('VA','ME') & Year >= 2019) |
#                     (STATE %in% c('ID','UT','NE') & Year >= 2020) |
#                     (STATE %in% c('OK','MO') & Year >= 2021) |
#                     (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
  #coeffs <- rbind(coeffs, model$coeftable[2,])
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH | ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
  coeffs <- rbind(coeffs, model$coeftable[1,])

@@

summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)), I( Pct.None  ) ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))

@@

```{r}
 did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ) , 
      yname = "ClinicHHI", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

    event_study(data = df.temptemp,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

 event_study(data = df.temptemp %>% filter(value_min == 1),
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

 event_study(data = df.temptemp,
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

  event_study(data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Att = ifelse(Att == 2010, 0, Att)),
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ), 
      yname = "Closed", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

@@

## TWFE First Stage
df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx) %>% ungroup() %>% filter(complete.cases(.))

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )

model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ factor(Year) + factor(ID))

@@

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
head(summary(reduced)$coeff) %>% as.data.frame()

reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
head(summary(reduced)$coeff) %>% as.data.frame()

reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
head(summary(reduced)$coeff) %>% as.data.frame()

@@

  ungroup() %>% 
  ###### MAJOR CHANGE: remove those CHCS wtih missing market share MS from GrantNumber
 #filter(!is.na(`MS`)) %>% 
  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
  rename(ID.chc = ID) %>% 
  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z) %>%
  arrange(`BHCMIS ID`, Zip, Year) %>% 
  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`)

@@

  df.z.temp2 <- df.z.temp #%>% filter(Att == 0 | Att > 2010)
  colnames(df.z.temp2)[k] <- "Outcome"
  model <-  did2s(
      data = df.z.temp2, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:8], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Estimate.1, `95% CI.1`)

@@

zip.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 2, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
  add_header_above(c(" " = 1, "Directly Competitive" = 2, "Indirectly Competitive" = 2)) %>% 
  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Zip Codes in Incumbent Clinics' Service Area" = 5))

@@

df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients)
df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)

@@

Takes a fair bit to run (~ 15 minutes)
```{r}

@@

## This next line takes a minute to run
zipdist <- df.z.temp %>%
  left_join(zipdist %>%
  select(BHCMISID.x, ZipCode) %>%
  unique(), by = c("BHCMIS ID" = "BHCMISID.x")) %>%
  select(`BHCMIS ID`, Zip, Att, DirectlyTreated, Tx, ZipCode) %>%
  unique()

@@

>>>>

coredata <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "HealthCenterInfo", skip = 0) %>% select(GrantNumber, FundingCHC:UrbanRuralFlag)

df.temptemp <- df.temptemp %>%
  left_join(uds.cw %>% filter(Year == 2011) %>% select(ModernGranteeID, BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>%
  left_join(coredata %>% select(GrantNumber, UrbanRuralFlag), by = c("ModernGranteeID" = "GrantNumber")) %>% 
  mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
                    (STATE %in% c('PA','IN','AK') & Year >= 2015) |
                    (STATE %in% c('MT','LA') & Year >= 2016) |
                    (STATE %in% c('VA','ME') & Year >= 2019) |
                    (STATE %in% c('ID','UT','NE') & Year >= 2020) |
                    (STATE %in% c('OK','MO') & Year >= 2021) |
                    (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
  #coeffs <- rbind(coeffs, model$coeftable[2,])
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH + UrbanRuralFlag| ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
  coeffs <- rbind(coeffs, model$coeftable[1,])

@@

summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% filter(value_min <= 2), 
              Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))

@@

```{r}
 did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ), 
      yname = "ClinicHHI", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

    event_study(data = df.temptemp,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

 event_study(data = df.temptemp %>% filter(value_min == 1),
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

 event_study(data = df.temptemp,
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

  event_study(data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Att = ifelse(Att == 2010, 0, Att)),
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0)) %>% filter(!is.na(Urban)), 
      yname = "Staff", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * value),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

es.direct <- did2s(
  data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) , 
  yname = "Qcomp", 
  treatment = "Tx",
  first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
    cluster_var = "ID", 
  verbose = TRUE)

cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
      cbind(Group = "Direct",es.direct$coeftable)) %>% 
  data.frame() %>% 
  mutate(estimate = as.numeric(Estimate), 
         std.error = as.numeric(Std..Error), 
         YearRel = as.numeric(YearRel)) %>% 
  filter(abs(YearRel) <= 6) %>% 
 ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

## TWFE First Stage
df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx, UrbanRuralFlag) %>% ungroup() %>% filter(complete.cases(.))

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ UrbanRuralFlag )

model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag+ factor(Year) + factor(ID))

@@

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
head(summary(reduced)$coeff) %>% as.data.frame()

reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
head(summary(reduced)$coeff) %>% as.data.frame()

reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
head(summary(reduced)$coeff) %>% as.data.frame()

@@

  ungroup() %>% 
  ###### MAJOR CHANGE: remove those CHCS wtih missing market share MS from GrantNumber
 #filter(!is.na(`MS`)) %>% 
  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
  rename(ID.chc = ID) %>% 
  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z, UrbanRuralFlag) %>%
  arrange(`BHCMIS ID`, Zip, Year) %>% 
  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag)

@@

  df.z.temp2 <- df.z.temp #%>% filter(Att == 0 | Att > 2010)
  colnames(df.z.temp2)[k] <- "Outcome"
  model <-  did2s(
      data = df.z.temp2, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
      #second_stage = ~ i(Tx , ref = FALSE)  + I(Tx * DirectlyTreated),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:8], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, `Pr...t..`, Estimate.1, `95% CI.1`, `Pr...t...1`)

@@

zip.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","p-value", "Estimate","95% CI", "p-value")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 2, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
  add_header_above(c(" " = 1, "Directly Competitive" = 3, "Indirectly Competitive" = 3)) %>% 
  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Zip Codes in Incumbent Clinics' Service Area" = 7))

@@

df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients, UrbanRuralFlag)
df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)

@@

@@

## This next line takes a minute to run
zipdist <- df.z.temp %>%
  left_join(zipdist %>%
  select(BHCMISID.x, ZipCode) %>%
  unique(), by = c("BHCMIS ID" = "BHCMISID.x")) %>%
  select(`BHCMIS ID`, Zip, Att, DirectlyTreated, Tx, ZipCode, UrbanRuralFlag) %>%
  unique()

@@

## Alt by year
Takes a couple minutes to run (~ 15)
